\documentclass[a4paper,12pt,oneside]{article}
\usepackage[top=3cm, bottom=2cm, left=3cm, right=2cm]{geometry}

\usepackage{units}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}

\pagenumbering{gobble}

\hypersetup{%
  colorlinks=true,% hyperlinks will be black
  linkcolor=blue,% hyperlink borders will be red
  urlcolor=blue,% hyperlink borders will be red
  linkbordercolor=blue,% hyperlink borders will be red
  pdfborderstyle={/S/U/W 1}% border style will be underline of width 1pt
}

\begin{document}
\author{Juan Lopes}

\begin{center}
	{\huge Hi, I'm Juan Lopes} \\[0.5cm]

	{\large \today}
\end{center}


\renewcommand{\abstractname}{}
\begin{abstract}
\noindent \begin{center}\textit{
Brazilian, lives in Rio de Janeiro. \\
Interested in algorithms, optimization, programming contests and serif typefaces. \\
B.S. in Computer Science; M.S. candidate in Computer Science. \\
Writes high-performance Java code at Intelie for the last 4 years. \\
Wrote beautiful C\# code at Living Consultoria for the 4 years before.
}
\end{center}
\end{abstract}


\section*{What excites me?}

	I love code in all its forms. Love writing and love reading. I'm a programmer
	since I was 9, when discovered that QBasic used to come with Windows 95.

	During the undergrad years, I had the chance to expand my interest in
	\textbf{algorithms}. There I was introduced to \textbf{programming contests}. I
	attended to six editions of \textbf{ICPC} (2007 to 2012), being
	\textbf{south-american finalist} in five of them. Also went to several editions of
	the \textbf{IEEEXtreme} competition. Our best results were \textbf{1\textsuperscript{st} place in Brazil} (2013) [\ref{url:ieeextreme7}]
	and \textbf{36\textsuperscript{th} place in the world} (2015) [\ref{url:ieeextreme9}].

	I like \textbf{Coding Dojos} a lot. Here in Rio, I help to organize the DojoRio
	[\ref{url:dojorio}] meetings. We probably have the most active Brazilian dojo
	community. As of today, there were \textbf{more than 250 sessions} (once a
	week, every wednesday). I think Coding Dojos are a great oportunity to try new
	languages, new problems and talk to great programmers.

	Recently, as a part of my work at \emph{Intelie}, I've been studying (and
	coding) a lot about \textbf{time-series analysis} and \textbf{real-time
	optimized algorithms}. As a result, I've been giving talks about it, from which
	I highlight the latest about \textbf{probabilistic data structures} (\emph{HyperLogLog}, \emph{Count-Min sketch}, etc.) at QCon São
	Paulo 2013 [\ref{url:qconsp2013}]. This is also the main topic of my master's thesis.

	Last, but not least, I have a strong presence in many programming communities, not only Java or C\# ones. My \textbf{GitHub} [\ref{url:github}] can show that I'm not shy to try new technologies. I also have \textbf{6,000+ reputation} points on \textbf{StackOverflow} [\ref{url:stackoverflow}], being half of this in the \emph{algorithms} tag.

\section*{Where did I work?}

\subsection*{Intelie \small{ (August 2011 -- Now)}}

	I currently work in the R\&D team at \textbf{Intelie}, a company focused in building tools for
	operation intelligence. There I write a lot of \textbf{Java} code. As a former
	C\# programmer, I'm surprisingly liking it.

	Most systems I write today use heavy backend algorithms to analyze real-time
	data streams at a rate of a \textbf{few terabytes per day}. Most of it would be
	impossible if we didn't use \textbf{distributed algorithms}.

	There I also had a very particular experience with \textbf{Lucene}, adapting
	its core to support indexing tens of billions of log messages per Lucene
	index, with sub-second distributed query, for the largest brazilian media
	group.
\subsection*{Living Consultoria \small{ (December 2007 -- July 2011)}}

	At \textbf{Living Consultoria} I was a mix of \textbf{lead developer} and
	\textbf{architect}. The focus of the company was Microsoft technologies, so I
	spent most of my time writing \textbf{C\#}, but I also worked with
	\textbf{Ruby} (on and off Rails) and some \textbf{PHP}. There I played a major
	role implementing the first projects using \textbf{Scrum} in the company (back
	in 2008, when it was still cool); participated in some \textbf{international
	projects}, collaborating with teams from many countries. Traveled to Amsterdam
	a couple of times, because of this.

\section*{Where did I study?}

	Today I'm a \textbf{Master's candidate} in \textbf{Computer Science} at
	\textbf{UERJ} (en: \emph{Rio de Janeiro State University}). It is one of the
	largest Brazilian universities. I'm currently writing about \textbf{probabilistic data structures}.

	I also have acquired my Bachelor's degree in Computer Science at \textbf{UERJ}.
	Finished in 2013. Actually I finished the regular course in 2009, but stayed
	there to be able to compete in the ICPC. I graduated with an essay about
	\textbf{polynomial-time regular expression implementations} [\ref{url:pyrex}].

\section*{How to find me?}

	As a true geek, I like smartphones. Android, mostly. So I will almost always
	have my phone with me, You can call me at \textbf{(+55) 21 99317 4772}.

	Probably the best way to find me is my e-mail
	[\href{mailto:me@juanlopes.net}{me@juanlopes.net}]. I'm also pretty active on
	Twitter [\href{http://twitter.com/juanplopes}{@juanplopes}].

\section*{Links}

	Some links are in portuguese.

\begin{enumerate}

  \item \label{url:ieeextreme7} \href{http://www.ieee.org/membership_services/membership/students/competitions/xtreme/xtreme7_final_rankings-country.pdf}{IEEEXtreme 7.0 results by country}
  
  \item \label{url:ieeextreme9} \href{http://www.ieee.org/xtreme}{IEEEXtreme 9.0 webpage (results pending)}
  
  \item \label{url:dojorio} \href{http://dojorio.org/}{DojoRio.org}
  \item \label{url:qconsp2013} \href{http://www.infoq.com/br/presentations/analisando-fluxo-dados-tempo-real}{QCon São Paulo 2013: Analyzing and Reducing Big Data Streams in Real-Time}
  \item \label{url:github} \href{https://github.com/juanplopes}{github.com/juanplopes}
  \item \label{url:stackoverflow} \href{http://stackoverflow.com/users/1327235/juan-lopes}{stackoverflow.com/users/1327235/juan-lopes}

  \item \label{url:pyrex} \href{http://github.com/juanplopes/pyrex}{github.com/juanplopes/pyrex}
  
  
\end{enumerate}

\end{document}

